\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-28 paper.tex
Added description for grid configurations
Correct spell mistake

The value for \(b_2\) is computed by fixing \(b_1\).

@@

Points are allocated to the bin that they fall in by considering the
nearest nearest centroid.

>>>>

The value for \(b_2\) is computed by fixing \(b_1\). Considering the
lower bound of the NLDR, \(a_1 > 2 \times s_1\) and
\(a_1 > \frac{1-s_1}{b_1 -1}\). The minimum \(a_1\) that satisfies the
constraints will be selected. For regular hexagons,
\(a_2 = \frac{2}{\sqrt(3)}a_1\). Therefore, \(a_2\) is computed for the
minimum \(a_1\). According to the upper bound of the NLDR,
\(b_2 = \left\lceil\frac{r_2 - s_2}{vs} + 1\right\rceil\), where
\(vs = \frac{a_2}{2} + \sqrt{{(\frac{a_2}{2})}^2 + {(\frac{a_1}{2})}^2}\).

@@

Points are allocated to the bin that they fall in by considering the
nearest centroid.
